\section{Introduction}
\label{mls:introduction}

In this Chapter we discuss the potential for future work and extensions of the prediction-based scheduler. Primarily we discuss the work involved with multi-level secure databases.

After the framework for transactional correctness has been developed (work published in \cite{ravan_ensuring_2020}) within the prediction-based solution we can then begin extending the two-dimensional categorization of the prediction-based scheduler to a categorization for multi-level secure database. The added dimension would include the security classification and allow for a much more robust decision-model. This portion of the overall solution would focus on multi-level secure database systems and covert timing channels. By providing a third dimension to the existing framework we can therefore extend our categorization structure. This allows us to provide a cover story for the timing difference of transactions with differing security classifications. 

The problem with multi-level secure databases is the possibility that there could be a covert channel allowing unauthorized access. The covert channel would provided the ability for a transaction of a lower security classification to access resources designed for a higher security classification. Existing research provides possible solutions but many of the solutions starve transactions of higher security classifications from gaining access to the resources needed (see Section \ref{mls:related_work}). With that cover story in mind we can then provide a solution that elevates high security transactions would the presence of a covert timing channel. With the prediction-based solution provided in Chapter \ref{chap:prediction_based_scheduler}, we can provide a cover story that determines locking priority based on the reputation of the transaction as a whole. This prevents the starvation of higher security classification transactions. By taking into consideration the security classification as a metric to calculate the reputation of the transaction, we also prevent the presence of covert channels. 