In this work, we have first analyzed the shortcomings to existing web service database transactions. These shortcomings involve the need for compensation transactions that, ultimately, are unnecessary overhead if \gls{acid} transaction properties can be leveraged. We analyzed the current solutions involving compensation transactions and maintaining consistency within a web service environment. As a result of this analysis, research and prototyping led to the development of a prediction-based solution. The final solution dynamically uses different concurrency control mechanisms depending on the attributes of the transaction. In the current work we have formally proven that this solution will ensure consistency by using dynamic concurrency control mechanisms (published in \cite{ravan_ensuring_2020}).

The next effort focused on the formal categorization of transactions before entering the prediction-based solution. Here we manage a reputation so that transactions can be rewarded or punished based on their performance in the system. Their reputations are built by using four attributes that rank them in the system: user ranking, commit ranking, efficiency ranking, and system ranking. From there we build a reputation score and prioritize well behaving transactions in the event of a conflict. We built a prototype to show how the solution compares against other solutions and discovered an increase in efficiency when systems contain 20\% or more conflicting transactions.

An additional effort of database recovery using provenance was completed (see \cite{theppatorn_2021}). 

Finally, we have proposed the needed extensions to the future work that will address three additional areas of improvement. The first area is expanding the prediction-based solution to a multi-level secure database environment where multiple security classifications exist. This involves extending the existing reputation score to contain an additional attribute to prevent the existence of covert timing channels that can appear due to differing security classifications. By doing so we provide a cover story for the transactional environment that enables the promotion of high security transactions without the disclosure of a covert timing channel.

Additional future work involves snapshot isolation, the prediction-based solution within linked databases, and providing the prediction-based solution within the an open source DBMS.

% The final effort will be the final extension leveraging all solutions. This effort will use Snapshot Isolation for low-performing and malicious transactions. With the current and proposed research the overall contribution will ensure consistency among web service transactions. The contribution will also minimize the effects of malicious and poorly performing transactions within a web service environment.