I would like to take this opportunity to thank the University of South Carolina for allowing me to complete my Ph.D. in Computer Science. It has been an amazing experience and I have been able to learn so much in the areas of Computer Science that will allow me to continue my contributions to the field in the future.

I would also like to thank The Citadel for their support during my tenure at University of South Carolina. While completing my degree through distance learning, The Citadel allowed me to use facilities and resources that allowed me to complete my degree program. The Citadel will always be my home and I will always be grateful for their support.

I personally want to thank my advisors Dr. Csilla Farkas and Dr. Shankar Banik. This has been a long journey and both of you have been there for me from the very beginning. There is no way to quantify the number of hours we have spent working on this contribution and both of you have been there to give the feedback that I needed no matter how hard it may have been.

I also want to thank Tidal Grounds coffee shop. With a family consisting of my wife and two young children it's hard to find the quiet time needed to dedicate toward a dissertation. Tidal Grounds not only provided me many caffeinated drinks and a quiet space, but I met many wonderful people who encouraged me and never let me give up. Without that support group this work would not have been made possible.

Last, but certainly not least, I want to thank my wife for her support through all the years. From the very first day when we decided together to embark on this journey you have always been there for me and given me the time I've needed to dedicate toward this work. This could not have been possible without you by my side each day.