\section{Dissertation Outline}
\label{diss:dissertation_outline}

\newcommand{\dissPhaseOne}
{\textbf{Transactional Correctness:} Consistency control algorithms prototyped and formally proven as a part of prediction-based solution (PBS). \textbf{Published in IEEE Transactions, February 2020}\newline}

\newcommand{\dissPhaseTwo}
{\textbf{Dissertation Proposal}}

\newcommand{\dissPhaseThree}
{\textbf{Dynamic Transaction Reputation:} Analyze and leverage reputation management solutions within PBS \textbf{Submit a conference paper\newline}}

\newcommand{\dissPhaseFour}
{\textbf{MLS Database Scheduling:} (extension area of PBS) scheduling of transactions based on existing metrics and security classification. \textbf{Submit a conference paper.}}

\newcommand{\dissPhaseFive}
{\textbf{Dissertation Defense}}

In this section we explain the full dissertation outline of what has already been accomplished, what is currently underway, and what is needed for the dissertation to be complete.

\subsection{Outline}

Table \ref{table:dissertation_outline} shows the progress made on the dissertation in all of its phases. Research began in August of 2014 after becoming enrolled as a student. I met with Dr. Farkas initially and began working on the transactional-correctness portion of the work that transitioned into the prediction-based scheduler. This is the work detailed in Chapter \ref{chap:prediction_based_scheduler}. The work underwent multiple revisions until we were confident with the solution and the form it has now taken. The work was completed and submitted to IEEE Transactions on Services Computing in April of 2019. In January of 2020, we received a decision of Accepted with Minor Revisions. Revisions were made and that has now been published. This serves as the bulk of the work and also the foundation of the extensions proposed in Chapters \ref{chap:multi_level_security} \& \ref{chap:dynamic_reputation}. Starting in February of 2020, we begin work on the multi-level secure databases and transactional reputation portion of the work. We plan to have both extensions completed by January of 2021 in order to officially defend and close out the dissertation.

\begin{table}
\centering
\renewcommand\arraystretch{1.4}
\captionsetup{singlelinecheck=false, labelfont=sc, labelsep=quad, justification=centering}
\caption{Outline}\vskip -1.5ex
\begin{tabular}{@{\,}r <{\hskip 2pt} !{\foo} >{\raggedright\arraybackslash}p{10cm}}
\toprule
\addlinespace[1.5ex]
February 2020 & \dissPhaseOne\\
August 2020 & \dissPhaseTwo\\
September 2020 & \dissPhaseThree\\
November 2020 & \dissPhaseFour\\
January 2021 & \dissPhaseFive\\
\end{tabular}
\label{table:dissertation_outline}
\end{table}